% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\usepackage{hyperref}
\usepackage{textcomp}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}    %uses new century schoolbook postscript font 
\pagestyle{plain} 
\pagenumbering{arabic}

\begin{document}

\name{Zeeve Rogoszinski}
% \address used twice to have two lines of address
%\address{3201 Belleview Ave., Cheverly, MD 20785}
\address{Phone: (516) 286-5149 $\bullet$ Email: zero@astro.umd.edu}

 
\begin{resume}

 
\section{EDUCATION} 
{\sl University of Maryland College Park - 2014-present} \\
				Masters in Astronomy - Awarded 2016\\
				PhD in Astronomy - Expected in 2020\\\\
{\sl Vassar College - 2010-2014} \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                BA in Astronomy \& Physics\\
              Study Abroad: University of Edinburgh \hfill Spring Semester 2013
 
\section{AWARDS \\ \& HONORS}
Ann G. Wylie Dissertation Fellowship \hfill Spring 2020 \\
NASA Earth and Space Science Fellowship (28 out of 180 selected) \hfill 2016 - present\\
Hartmann Student Travel Grant for Division of Planetary Science meeting	\hfill 2016\\
{ Vassar College Departmental Honors in Astronomy} \hfill 2014\\
{ Vassar College Departmental Honors in Physics} \hfill 2014\\
{ Vassar College General Honors} \hfill 2014\\     
{ Sigma Xi} \hfill 2014\\ 
{ Ethel Hickox Pollard Memorial Physics Award} \hfill 2013 \\                 
{ Janet Murray '31 Memorial Scholarship} \hfill 2013
 
\section{RESEARCH}
{\sl University of Maryland} \hfill 2015-present\\
Topic: The Tilts and Spins of Planets and Moons\\
Advisor: Dr. Douglas Hamilton\\
Summary: My dissertation's primary focus is on the origin of Uranus' 98\textdegree~tilt within the context of ice giant formation. I used an N-body integrator (HNBody) to calculate the motions of the planets, and wrote numerical tools in C to calculate a planet's spin-state as a product of collisions or a secular spin-orbit resonance. My research has expanded to using hydrodynamic simulations (DISCO) to analyze the final spin periods of gas giants, and to explore how collisions may have shaped the orbital architectures of irregular satellite systems.

Talks:
\begin{itemize}
\item ``Using collisions and resonances to tilting Uranus" at the 231\textsuperscript{st} AAS meeting
\item ``Continuing the investigation to tilting Uranus with a secular spin-orbit resonance" at the 49\textsuperscript{th} DPS meeting
\item ``Tilting Uranus without a Collision" at the 5\textsuperscript{th} AstroCon DC meeting
\end{itemize}
Poster:
\begin{itemize}
\item ``How do collisions shape the orbits of irregular satellites?" at the 50\textsuperscript{th} DPS meeting
\item ``Why is it so difficult to tilt Uranus?" at the 50\textsuperscript{th} DDA meeting
\item ``Tilting Uranus without a Collision" at the 48\textsuperscript{th} DPS meeting

\end{itemize}

{\sl NASA GSFC Summer Internship} \hfill 2014\\
				Topic: Constraining cosmic ray origins through spectral radio breaks in supernova remnants.\\
				Advisor: Dr. John Hewitt\\
Summary: I wrote a Python code to analyze Planck and WMAP data and compile a spectrum for supernova remnants as possible sources for cosmic rays.\\
Poster: ``Constraining Cosmic Ray Origins Through Spectral Radio Breaks In Supernova Remnants" at the 225\textsuperscript{th} AAS meeting.

				
{\sl Senior Thesis} \hfill 2013-2014 \\
				Topic: Analyzing structure and activity in Hubble Deep Field elliptical
galaxies. \\
Advisor: Dr. Debra Elmegreen\\
Summary: I used IRAF to conduct unsharp masking, take radial profiles, and conduct basic photometry of multiple elliptical galaxies in order to understand their internal structures as possible indicators of their formation histories.
				
{\sl Keck Northeast Astronomy Consortium Summer Research Fellow} \hfill 2013 \\
				Topic: Analyzing the causes of the black-drop effect observed during the 2012 Venus transit at Williams College.\\
				Advisor: Dr. Jay M. Pasachoff\\
Presentation: Keck Northeast Astronomy Consortium Student Research Symposium at Vassar College.

Posters:
\begin{itemize}
\item ``Observations of the Black-Drop Effect at the 2012 Transit of Venus" at the 223\textsuperscript{rd} AAS meeting.
\item ``Recent KBO (Pluto/Charon and beyond, including Quaoar) Occultation Observations by the Williams College Team as part of the Williams-MIT Collaboration" at the 45\textsuperscript{th} DPS meeting
\end{itemize}

				
{\sl Optical Science Center for Applied Research Summer Internship} \hfill 2012 \\
                Topic: Reduced LIBS (Laser-induced breakdown spectroscopy) data for iron samples under Mars-like conditions in preparation for the Mars Science Laboratory.\\  
                Advisor: Dr. Noureddine Melikechi - Delaware State University\\
Other: Using Gaussian Optics Theory and ABCD Matrix Theory to figure out the correct focal lengths of lenses for a beam expander that will be used in future experiments.
                 
{\sl Vassar College Observatory} \hfill 2010-2012 \\
               Topic: Observing the periodicities of contact binary star systems VW Cep, OO Agr, Zeta Tauri, and Beta Lyrae using both photometry and spectroscopy methods from data taken at the Vassar College Observatory\\
                Advisor: Dr. Fred Chromey
                
\section{TEACHING} 
Teaching assistant at University of Maryland for Astronomy 101 \hfill 2014-2016\\
Academic Astronomy Intern at Vassar College \hfill 2013-2014 \\
Teaching assistant at the Williams College Planetarium \hfill 2013
				\\
Narrator of the movie ``Colors and Motions of the Sun" \hfill 2013\\
\setlength{\parindent}{.88cm}
				\indent Created by Professor Jay M. Pasachoff of Williams College \\	
				\indent	\url{http://www.youtube.com/watch?v=ym3WOA2GzFI}
				\\
Teaching Assistant at the Community Hebrew School in Poughkeepsie, NY \hfill  2012

\section{RELEVANT \\ SKILLS} 
\noindent {\sl Software:} Jupyter, IRAF, ImageJ, DS9, Microsoft Office. \\
                {\sl Languages:} C, Python, Mathematica, LaTeX. \\
                {\sl Telescope Maintenance:} Vassar College Observatory\\

\section{ACTIVITIES}
\noindent Executive Secretary for NASA \hfill 2017, 2018 \\
\noindent GRAD-MAP member and volunteer \hfill 2015-present  \\
Society of Physics Students (SPS) member \hfill 2010-2014
                
\end{resume}
\end{document}